?apply family
========================================================

This document shows some examples of how to use ?apply

```{r}
class1 <- data.frame('name'=c('John','Jane','Jraps','Jwchit'),
          'height'=c(130,180,200,196))
class2 <- data.frame('name'=c('Kohn','Kane','Kraps'),
          'height'=c(120,150,130))
L <- list("class1"=class1,"class2"=class2)

## Let's define a function to calculate the mean height
meanHeight <- function(df) {
        mean(df$height, na.rm=T)
}
```

lapply
========================================================
First, let's look at lapply
LAPPLY -- loop over and apply a function on each element in a list, and always return a list

```{r}
lapply.result <- lapply(X=L, FUN=meanHeight)
class(lapply.result)
print(lapply.result)
```

Each output list element can have different length
```{r}
v <- 1:5
lapply(v,runif)
```

sapply
========================================================
Now try sapply
SAPPLY -- same to LAPPLY but will simplify the output

```{r}
sapply.result <- sapply(X=L, FUN=meanHeight)
class(sapply.result)
print(sapply.result)
```

In case that each output has different length, the simplest form to contain such output is a list.
So, sapply will output a list each of whose elements has different length instead.
```{r}
v <- 1:5
sapply(v,runif)
```

apply
========================================================
APPLY -- collapse a dimension of an array by a function
```{r}
myArray <- array(1:24, c(2,3,4))
## we want to find max over the third dimension, and preserve the first and second dim.
apply(X=myArray, MARGIN=c(1,2), FUN=max)
## a simpler example
m1 <- myArray[,,1]
apply(m1, 1, sum)
apply(m1, 2, sum)
```